Topological Equivariant Artist Model

### 2022-01-06 slides/main.tex
reworking functor
sheaf reworking

\usepackage{appendixnumberbeamer} 
\usepackage{comment}
\usepackage{minted}
\setminted[python]{fontsize=\scriptsize, 
                   linenos,
                   numbersep=8pt,
                   autogobble, 
                   frame=lines,
                   bgcolor=bg,
                   framesep=3mm} 
\usepackage{notation} % move this later

@@

\begin{frame}{Fiber Bundles}
    \begin{columns}
        \column{0.39\textwidth}
            \begin{equation*}
                %\label{eq:related-work:continuity:fiber-bundle}
                \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
                  \onslide*<2-|handout:1>{\dfiberc} 
                  \onslide*<4-|handout:1>{\arrow[r, hook]} \& 
                  \onslide*<3|handout:1>{\dtotalc} 
                  \onslide*<4-|handout:1>{\arrow[d, "\pi"']} \\
                   \& \onslide*<1-|handout:1>{\dbasec} 
                   \onslide*<5-|handout:1>{\arrow[u, "\dsectionc \in \cgamma{\dbasec}{\dtotalc}"', bend right, pos=.5]}
                \end{tikzcd}
            \end{equation*}
     \column{0.59\textwidth}
        \begin{description}
            \item<1-|handout:1>[\textcolor{base}{Base Space}] $( \dbasec, \mathcal{T})$, $\dbasepointc \in \opensetc \subset \dbasec$
            \item<2-|handout:1>[\textcolor{fiber}{Fiber Space}] $\dfiberc_{\dbasepointc} = \pi^{-1}(\dbasepointc)$
            \item<3-|handout:1>[\textcolor{total}{Total Space}]  $\dtotalc\restriction_{\opensetc} = \dbasec\restriction_{\opensetc} \times \dfiberc\restriction_{\opensetc}$ \\ for all $\opensetc \subset K$ 
        \end{description}
    \end{columns}
    \pause
    \begin{alertblock}<5-|handout:1>{Sections}
    $\cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} \coloneqq \big\{\dsectionc: \opensetc\rightarrow \dtotalc\restriction_{\openset} \; \bigm{\vert} \pi(\dsectionc(\dbasepointc)) = \dbasepointc\;for\, all\; \dbasepointc \in \opensetc \big\}$
    \end{alertblock}
\end{frame}

\subsection{Category Theory}

@@

\begin{frame}{$\mathcal{C}^{op}$}
    \begin{columns}
        \column{0.29\textwidth}
        \begin{tikzcd}[ampersand replacement=\&]
            \opensetc_1 \arrow[r, "\iota_{1,2}", color=base] \arrow[rd, "\iota_{1,2}\circ \iota_{2,3}"', color=base] \arrow["id_{\opensetc_1}"', loop, distance=2em, in=215, out=145, color=base] \& \opensetc_2 \arrow[d, "\iota_{2,3}", color=base] \arrow["id_{\opensetc_2}"', loop, distance=2em, in=125, out=55, color=base] \\
        \& \opensetc_3 \arrow["id_{\opensetc_3}"', loop, distance=2em, in=305, out=235, color=base]              
    \end{tikzcd}
        \column{0.69\textwidth}
        \onslide<2-|handout:1>{
            \begin{tikzcd}[ampersand replacement=\&]
            \cgamma{\opensetc_1}{\dtotalc\restriction_{\opensetc_1}} \&  \& \cgamma{\opensetc_2}{\dtotalc\restriction_{\opensetc_2}} \arrow[ll, "\iota^*\restriction_{\opensetc_1}"', color=set]\\
            \&\&\\\&  \& \cgamma{\opensetc_3}{\dtotalc\restriction_{\opensetc_3}} \arrow[uu, "\iota^*\restriction_{\opensetc_2}"', color=set] \arrow[lluu, "\iota^*\restriction_{\opensetc_2} \circ \iota^*\restriction_{\opensetc_1}", color=set]
            \end{tikzcd}
        }

@@

\begin{frame}{Functor $\textcolor{functor}{\bm{F}}: \textcolor{source}{\mathcal{C}} \rightarrow \textcolor{target}{\mathcal{D}}$}
\begin{columns}
    \column{.39\textwidth}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement = \&, ]
            \onslide*<1-|handout:1>{\textcolor{source}{c}} 
            \onslide*<1-|handout:1>{\arrow[d, "f"', shift right=0, color=source]} 
            \onslide*<3-|handout:1>{\arrow[r, "F", color=functor, maps to]} \& 
            \onslide*<2-3|handout:0>{\textcolor{target}{d}}
            \onslide*<4|handout:0>{\textcolor{target}{F(c)}} 
            \onslide*<0|handout:1>{\textcolor{target}{F(c)=d}} 
            \onslide*<2|handout:0>{\arrow[d, shift right=0, color=target]}
            \onslide*<3-|handout:0>{\arrow[d, "F(f)", shift right=0, color=target]}
            \onslide*<0|handout:1>{\arrow[d, "F(f)", shift right=3, color=target]} \\
            \onslide*<1-|handout:1>{\textcolor{source}{c^{\prime}}} 
            \onslide*<3-|handout:1>{\arrow[r, "F"', color=functor, maps to]}\& 
            \onslide*<2-3|handout:0>{\textcolor{target}{d^{\prime}}}
            \onslide*<4-|handout:0>{\textcolor{target}{F(c^{\prime})}}
            \onslide*<0|handout:1>{\textcolor{target}{F(c^{\prime})= d^{\prime}}}                    
        \end{tikzcd}
    \end{equation*}
    \column{.59\textwidth}
    \begin{alertblock}<5-|handout:1>{composition}
    $\textcolor{functor}{F}(\textcolor{source}{g}) \circ  \textcolor{functor}{F}(\textcolor{source}{f}) = \textcolor{functor}{F} (\textcolor{source}{g}\circ \textcolor{source}{f})$
    \end{alertblock}
    \begin{alertblock}<6-|handout:1>{identity}
    $\textcolor{functor}{F}(\textcolor{source}{id_c}) = \textcolor{target}{id}_{\textcolor{functor}{F}(\textcolor{source}{c})}$
    \end{alertblock}
\end{columns}
\end{frame}

\begin{frame}{Presheaf: $\sheafc: \mathcal{C}^{op} \textcolor{sheaf}{\rightarrow} \setc $}
    \begin{columns}
    \column{0.29\textwidth}
    \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
        \onslide*<9-|handout:1->{\dfiberc}
        \onslide*<9-|handout:1->{\arrow[r, hook]} \& 
        \onslide*<1-|handout:1->{\dtotalc}
        \onslide*<1-|handout:1->{\arrow[d, "\pi"']} \\
           \& 
        \onslide*<1-|handout:1->{\dbasec}
        \onslide*<3-|handout:1->{\arrow[u, "\dsectionc \in \cgamma{\dbasec}{\dtotalc}"', bend right, pos=.5]}
        \end{tikzcd}
    \column{0.69\textwidth}
        \begin{tikzcd}[ampersand replacement = \&, column sep=small]
            \onslide*<3,6-|handout:0>{{\cgamma{\opensetc_1}{\dtotalc\restriction_{{\opensetc_1}}}}} 
            \onslide*<4-5|handout:0>{{\cgamma{\opensetc_1}{\dtotalc\restriction_{{\opensetc_1}}}}\in \setc}
            \onslide*<0|handout:1>{\setc \ni {\cgamma{\opensetc_1}{\dtotalc\restriction_{{\opensetc_1}}}}}
            \&  
            {} \& 
            \onslide*<6-|handout:1>{{\cgamma{\opensetc_2}{\dtotalc\restriction_{\opensetc_2}}}} 
            \onslide*<7-|handout:1>{\arrow[ll, "\iota^*"', hook', color=set]} \\\& \&\\
            \onslide*<3|handout:0>{\opensetc_1 \subset \dbasec}
            \onslide*<4-5|handout:0>{\opensetc_1 \in Ob(\mathcal{\dbasec}^{\textcolor{base}{op}})}
            \onslide*<6-|handout:0>{\opensetc_1}
            \onslide*<0|handout:1>{Ob(\mathcal{\dbasec}^{\textcolor{base}{op}}) \ni \opensetc_1} 
            \onslide*<5-|handout:0>{\arrow[uu, "\sheafc_{\dbasec}", maps to, color=sheaf]}
            \onslide*<0|handout:1>{\arrow[uu, "\sheafc_{\dbasec}", maps to, color=sheaf, shift right = 10]}
            \onslide*<7-|handout:1>{\arrow[rr, "\iota"', hook, color=base]} \&   
            \onslide*<8-|handout:1>{\arrow[uu, "\sheafc_{\dbasec}" description, maps to, color=sheaf]} \& 
            \onslide*<6-|handout:1>{\opensetc_2} 
            \onslide*<6-|handout:1>{\arrow[uu, "\sheafc_{\dbasec}"', maps to, color=sheaf]}                   
            \end{tikzcd}
    \end{columns}
    \begin{description}
        \item<8-|handout:1>[stalk]$\sheafc(\dbasec)\restriction_{\dbasepointc}\coloneqq \lim\limits_{\opensetc\ni \dbasepointc} \Gamma(\opensetc, \dtotalc\restriction_{\opensetc}) \approx \dfiberc_{\dbasepointc}$
        \item<9-|handout:1>[germ]   $\dsectionc(\dbasepointc) \in \sheafc_{\dbasec}$
    \end{description}
\end{frame}

\begin{frame}{Sheaves}
    A sheaf is a presheaf that satisfies the following two axioms

    \onslide<2-|handout:2->{Given open cover $\mathcal{\opensetc} = \{\opensetc_i\}_{i\in I}$ of $\opensetc$:}
    \begin{block}<3-|handout:3->{locality}
    $\dsectionc^{1}, \dsectionc^{2} \in \sheafc(\opensetc_i)\\ \dsectionc^{1}\restriction_{\opensetc_i} = \dsectionc^{2}\restriction_{\opensetc_i} \implies \dsectionc^{1} = \dsectionc^{2}$
    \end{block} 
    \begin{block}<4-|handout:4>{gluing}
    $\dsectionc_{i} \in \sheafc(\opensetc_i), \dsectionc_{j} \in \sheafc(\opensetc_j), \opensetc_i, \opensetc_j \in \mathcal{U}\\ \dsectionc_{i}\restriction_{\opensetc_i\cap \opensetc_j} = \dsectionc_{j}\restriction_{\opensetc_i \cap \opensetc_j} \implies \dsectionc\restriction_{\opensetc_i} = \dsectionc_i$ 
    \end{block}      
\end{frame}

\begin{frame}{
\only<-8|handout:-8>{Morphism of sheaves:}
\only<5-6|handout:5-6>{pullback}
\only<7|handout:7>{pushforward} 
\only<8,11-|handout:8,11->{pullback \& pushforward}
\only<9|handout:9>{pullback sections}
\only<10|handout:10>{pushforward sections}
}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
            \onslide*<7-8|handout:7-8>{\sheafc_{\gbasec}(\gbasec)} 
            \onslide*<10-|handout:10->{\{\gsectionc: \gbasepointc \scarr \setc \}}
            \onslide*<7-8,10-|handout:7-8,10->{\arrow[rr, "\textcolor{functor}{\vindexpush}", color=functor]} \& \& 
            \onslide*<7-8|handout:7-8>{(\textcolor{functor}{\vindexpush}\sheafc_{\gbasec})(\dbasec)}  
            \onslide*<10-|handout:10->{(\textcolor{functor}{\vindexpush}\gsectionc:\dbasepointc \scarr \setc)}
            \\
            \onslide*<2-8|handout:2-8>{\gbasec}
            \onslide*<9-|handout:9->{\gbasepointc}
            \onslide*<3-|handout:3->{\arrow[rr, "\vindex", color=functor]}
            \onslide*<7-8,10-|handout:7-8,10->{\arrow[u, "\sheaf_{\gbasec}", color=sheaf]}
            \onslide*<6,8-9,11-|handout:6,8-9,11->{\arrow[d, dashed, color=sheaf]} \&  \& 
            \onslide*<1-8|handout:1-8>{\dbasec}
            \onslide*<9-|handout:9->{\dbasepointc}
            \onslide*<4-6,8-9,11-|handout:4-6,8-9,11->{\arrow[d, "\sheaf_{\dbasec}", color=sheaf]}
            \onslide*<7-8,10-|handout:7-8,10->{\arrow[u, dashed, color=sheaf]} \\
            \onslide*<5-6,8|handout:5-6,8>{(\textcolor{functor}{\vindexpull}\sheafc_{\dbasec})(\gbasec)} 
            \onslide*<9,11-|handout:9,11->{\{\textcolor{functor}{\vindexpull}\dsectionc:\gbasepointc\scarr\setc\}}
            \onslide*<5-6,8-9,11-|handout:5-6,8-9,11->{\arrow[rr, "\textcolor{functor}{\vindexpull}", color=functor]}  \& \& 
            \onslide*<4-6,8|handout:4-6,8>{\sheafc_{\dbasec}(\dbasec)}                      
            \onslide*<9,11-|handout:9,11->{\{\dsectionc: \dbasepointc \scarr \setc \}}
        \end{tikzcd}
    \end{equation*}
    \onslide<9,11-|handout:9,11->{
        \begin{equation*}
            \dsectionc^{\textcolor{functor}{*}}(\gbasepointc) = \dsectionc(\textcolor{functor}{\vindex}(\gbasepointc)) = \dsectionc(\dbasepointc)
        \end{equation*}
    }
    \onslide<10-|handout:10,11->{
        \begin{equation*}
            \gsectionc(\gbasepointc) = \gsectionc_{\textcolor{functor}{*}}(\dbasepointc) = \gsectionc(\textcolor{functor}{\vindexpre}(\dbasepointc))
        \end{equation*}
    }
\end{frame}

\begin{frame}{
    \only<1-3|handout:1-3>{Pullback \& Pushforward are Isomorphic}
    \only<4|handout:4>{$\vartistc:\sheafc_{\dbasec}\rightarrow \sheafc_{\gbasec}$}
    \only<5-|handout:5->{$\vartistc: \dsectionc \mapsto \gsectionc$}
    }
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&]
          \onslide*<1-4|handout:1-4>{\sheafc_{\gbasec}(\gbasec)} 
          \onslide*<5-|handout:5->{\{\gsectionc:\gbasepointc \scarr \setc\}}
          \onslide*<1-3|handout:1-3>{\arrow[rr, "\textcolor{functor}{\vindexpush}", color=functor]}  
          \onslide*<4-|handout:4->{\arrow[rr, "\vindexpushc", color=artist]} 
          \& \& 
          \onslide*<1-4|handout:1-4>{(\textcolor{functor}{\vindexpush}\sheafc_{\gbasec})(\dbase)}
          \onslide*<5-|handout:5>{\{\vindexpushc \gsectionc: \dbasepointc \scarr\setc\}}
          \\
          \& \& \\
          \onslide*<1-4|handout:1-4>{(\textcolor{functor}{\vindexpull}\sheafc_{\dbase})(\gbasec)}
          \onslide*<5-|handout:5>{\{ \vindexpullc\dsectionc:\gbasepointc\scarr \setc\}}
          \onslide*<1-3|handout:1-3>{\arrow[rr, "\textcolor{functor}{\vindexpull}", color=functor]}
          \onslide*<4-|handout:4->{\arrow[rr, "\vindexpullc", color=artist]}
          \onslide*<2-3|handout:2-3>{\arrow[uu, "\textcolor{homset}{hom_{\gbasec}}", color=homset]} 
          \onslide*<4-|handout:4->{\arrow[uu, "\vartistc_{\vindexpushc}", color=artist]}
          \&  \& 
          \onslide*<1-4|handout:1-4>{\sheafc_{\dbase}(\dbase)} 
          \onslide*<5-|handout:5->{\{\dsectionc:\dbasepointc \scarr \setc\}}
          \onslide*<2-3|handout:2-3>{\arrow[uu, "\textcolor{homset}{hom_{\dbasec}}"', color=homset]}
          \onslide*<4-|handout:4->{\arrow[uu, "\vartistc_{\vindexpullc}"', color=artist]}
          \onslide*<3|handout:3>{\arrow[lluu, "\textcolor{homset}{hom_{\dbasec,\gbasec}}"' description, dashed, color=homset]}
          \onslide*<4-|handout:4->{\arrow[lluu, "\vartistc"' description, dashed, color=artist]}
        \end{tikzcd}
      \end{equation*}

>>>>

\usepackage{appendixnumberbeamer} 
\usepackage{comment}
\usepackage{minted}
\setminted[python]{fontsize=\scriptsize, 
                   linenos,
                   numbersep=8pt,
                   autogobble, 
                   frame=lines,
                   bgcolor=bg,
                   framesep=3mm}

\usepackage{notation} % move this later

@@

\begin{frame}
    \frametitle<1|handout:1>{Fiber Bundle}
    \frametitle<6|handout:2>{Data Bundle}
    \frametitle<7|handout:3>{Graphic Bundle}
    \begin{columns}
        \column{0.39\textwidth}
            \begin{equation*}
                %\label{eq:related-work:continuity:fiber-bundle}
                \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
                  \onslide*<2-6|handout:1-2>{\dfiberc}
                  \onslide*<7|handout:3>{\gfiberc} 
                  \onslide*<4-|handout:1->{\arrow[r, hook]} \& 
                  \onslide*<3-6|handout:1-2>{\dtotalc} 
                  \onslide*<7|handout:3>{\gtotalc}
                  \onslide*<4-|handout:1->{\arrow[d, "\pi"']} \\
                   \& 
                   \onslide*<1-6|handout:1-2>{\dbasec}
                   \onslide*<7|handout:3>{\gbasec} 
                   \onslide*<5-6|handout:1-2>{\arrow[u, "\dsectionc \in \cgamma{\dbasec}{\dtotalc}"', bend right, pos=.5]}
                   \onslide*<7|handout:3>{\arrow[u, "\gsectionc \in \cgamma{\gbasec}{\gtotalc}"', bend right, pos=.5]}
                \end{tikzcd}
            \end{equation*}
     \column{0.59\textwidth}
     \only<1-5|handout:1>{
        \begin{description}
            \item<1-5|handout:1>[\textcolor{base}{Base Space}]{$( \dbasec, \mathcal{T})$, $\dbasepointc \in \opensetc \subset \dbasec$}
            \item<2-5|handout:1>[\textcolor{fiber}{Fiber Space}]{$\dfiberc\restriction_{\dbasepointc} = \pi^{-1}(\dbasepointc)$}
            \item<3-5|handout:1>[\textcolor{total}{Total Space}]{ $\dtotalc\restriction_{\opensetc} = \dbasec\restriction_{\opensetc} \times \dfiberc\restriction_{\opensetc}$ \\ for all $\opensetc \subset K$}
        \end{description}}
    \only<6|handout:2>{
        \begin{description}
            \item[\textcolor{base}{Continuity Type \dbasec}]{how data elements are organized (topological properties) \cite{wilkinsonGrammarGraphics2005})}
            \item[\textcolor{fiber}{Fields Type \dfiberc}] {generalization of a schema - named and typed date fields \cite{spivakSIMPLICIALDATABASES, spivakDatabasesAreCategories2010}}
            \item[\textcolor{total}{Data Type \dtotalc}]{continuity type + field type}
        \end{description}
        }
        \only<7|handout:3>{
            \begin{description}
                \item[\textcolor{base}{Continuity Type \gbasec}]{how pixels are organized in the display space}
                \item[\textcolor{fiber}{Display Type \gfiberc}] {display specifications}
                \item[\textcolor{total}{Graphic Type \gtotalc}]{continuity type + display type}
            \end{description}
            }
    \end{columns}
    \pause
    \only<5|handout:1>{
        \begin{alertblock}{Sections}
            \begin{aligned*}         
        \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} \coloneqq \big\{\dsectionc: \opensetc\rightarrow \dtotalc\restriction_{\opensetc} \; \bigm{\vert} \pi(\dsectionc(\dbasepointc)) = \dbasepointc\;for\, all\; \dbasepointc \in \opensetc \big\}
        \end{aligned*}
        \end{alertblock}
    }
    \only<6|handout:2>{
    \begin{alertblock}{Data \cite{butlerVisualizationModelBased1989,butlerVectorBundleClassesForm1992}}
        \begin{aligned*}
        \dsectionc(\dbasepointc) = &\delementc,\; \dbasepointc\in \opensetc\subset \dbasec,\; \delement \in \dfiberc\restriction_{\dbasepointc}\\
        &\delementc=\{field_0:value, \cdots field_i:value, \cdots field_n:value\}
        \end{aligned*}
    \end{alertblock}
    }
    \only<7|handout:3>{
        \begin{alertblock}{Graphic}
            \begin{aligned*}         
            \cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}} \coloneqq \big\{\gsectionc: \opensetgc\rightarrow \gtotalc\restriction_{\opensetgc} \; \bigm{\vert} \pi(\gsectionc(\gbasepointc)) = \gbasepointc\;for\, all\; \gbasepointc \in \opensetgc \big\}\\
            \vspace{5pt}\\
            \gsectionc(\gbasepointc) = d,\; \gbasepointc\in \opensetgc\subset \gbasec,\; d \in \dfiberc\restriction_{\gbasepointc}\\
            for\;example:\; d=\{x,\,y,\,r,\,g,\,b\}
        \end{aligned*}
    \end{alertblock}
    }

\subsection{Category Theory}
\begin{frame}[fragile]{}
    \begin{minted}{python}
        Artist(data:Data) -> Graphic
    \end{minted}
\end{frame}

@@

\begin{frame}{$\mathcal{C}^{op}$}
    \begin{columns}
        \column{0.29\textwidth}
        \begin{tikzcd}[ampersand replacement=\&]
            \opensetc_1 \arrow[r, "\iota_{1,2}", color=base] \arrow[rd, "\iota_{1,2}\circ \iota_{2,3}"', color=base] \arrow["id_{\opensetc_1}"', loop, distance=2em, in=215, out=145, color=base] \& \opensetc_2 \arrow[d, "\iota_{2,3}", color=base] \arrow["id_{\opensetc_2}"', loop, distance=2em, in=125, out=55, color=base] \\
        \& \opensetc_3 \arrow["id_{\opensetc_3}"', loop, distance=2em, in=305, out=235, color=base]              
    \end{tikzcd}
        \column{0.69\textwidth}
        \onslide<2-|handout:1>{
            \begin{tikzcd}[ampersand replacement=\&]
            \cgamma{\opensetc_1}{\dtotalc\restriction_{\opensetc_1}} \&  \& \cgamma{\opensetc_2}{\dtotalc\restriction_{\opensetc_2}} \arrow[ll, "\iota^*\restriction_{\opensetc_1}"', color=set]\\
            \&\&\\\&  \& \cgamma{\opensetc_3}{\dtotalc\restriction_{\opensetc_3}} \arrow[uu, "\iota^*\restriction_{\opensetc_2}"', color=set] \arrow[lluu, "\iota^*\restriction_{\opensetc_2} \circ \textcolor{set}{\iota^*\restriction}_{\opensetc_1}", color=set]
            \end{tikzcd}
        }

@@

\begin{frame}{Functor $\textcolor{functor}{\bm{F}}: \textcolor{source}{\mathcal{C}} \rightarrow \textcolor{target}{\mathcal{D}}$}
\begin{columns}
    \column{.39\textwidth}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement = \&, ]
            \onslide*<1-|handout:1>{\textcolor{source}{c}} 
            \onslide*<1-|handout:1>{\arrow[d, "f"', shift right=0, color=source]} 
            \onslide*<3-|handout:1>{\arrow[r, "F", color=functor, maps to]} \& 
            \onslide*<2-3|handout:0>{\textcolor{target}{d}}
            \onslide*<4-|handout:0>{\textcolor{target}{F(c)}} 
            \onslide*<0|handout:1>{\textcolor{target}{F(c)=d}} 
            \onslide*<2|handout:0>{\arrow[d, shift right=0, color=target]}
            \onslide*<3-|handout:0>{\arrow[d, "F(f)", shift right=0, color=target]}
            \onslide*<0|handout:1>{\arrow[d, "F(f)", shift right=3, color=target]} \\
            \onslide*<1-|handout:1>{\textcolor{source}{c^{\prime}}} 
            \onslide*<3-|handout:1>{\arrow[r, "F"', color=functor, maps to]}\& 
            \onslide*<2-3|handout:0>{\textcolor{target}{d^{\prime}}}
            \onslide*<4-|handout:0>{\textcolor{target}{F(c^{\prime})}}
            \onslide*<0|handout:1>{\textcolor{target}{F(c^{\prime})= d^{\prime}}}                    
        \end{tikzcd}
    \end{equation*}
    \column{.59\textwidth}
    \begin{alertblock}<5-|handout:1>{composition}
        \begin{aligned*}
            \textcolor{functor}{F}(\textcolor{source}{g}) \circ  \textcolor{functor}{F}(\textcolor{source}{f}) = \textcolor{functor}{F} (\textcolor{source}{g}\circ \textcolor{source}{f})
        \end{aligned*}
    \end{alertblock}
    \begin{alertblock}<6-|handout:1>{identity}
        \begin{aligned*}
            \textcolor{functor}{F}(\textcolor{source}{id_c}) = \textcolor{target}{id}_{\textcolor{functor}{F}(\textcolor{source}{c})}
        \end{aligned*}
    \end{alertblock}
\end{columns}
\end{frame}

\begin{frame}{Presheaf: $\sheafc: \mathcal{C}^{op} \textcolor{sheaf}{\rightarrow} \setc $}
    \begin{columns}
    \column{0.29\textwidth}
    \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
        \onslide*<9-|handout:1->{\dfiberc}
        \onslide*<9-|handout:1->{\arrow[r, hook]} \& 
        \onslide*<1-|handout:1->{\dtotalc}
        \onslide*<1-|handout:1->{\arrow[d, "\pi"']} \\
           \& 
        \onslide*<1-|handout:1->{\dbasec}
        \onslide*<3-|handout:1->{\arrow[u, "\dsectionc \in \cgamma{\dbasec}{\dtotalc}"', bend right, pos=.5]}
        \end{tikzcd}
    \column{0.69\textwidth}
        \begin{tikzcd}[ampersand replacement = \&, column sep=small]
            \onslide*<3,6-|handout:0>{{\cgamma{\opensetc_1}{\dtotalc\restriction_{{\opensetc_1}}}}} 
            \onslide*<4-5|handout:0>{{\cgamma{\opensetc_1}{\dtotalc\restriction_{{\opensetc_1}}}}\in \setc}
            \onslide*<0|handout:1>{\setc \ni {\cgamma{\opensetc_1}{\dtotalc\restriction_{{\opensetc_1}}}}}
            \&  
            {} \& 
            \onslide*<6-|handout:1>{{\cgamma{\opensetc_2}{\dtotalc\restriction_{\opensetc_2}}}} 
            \onslide*<7-|handout:1>{\arrow[ll, "\iota^*"', hook', color=set]} \\\& \&\\
            \onslide*<3|handout:0>{\opensetc_1 \subset \dbasec}
            \onslide*<4-5|handout:0>{\opensetc_1 \in Ob(\mathcal{\dbasec}^{\textcolor{base}{op}})}
            \onslide*<6-|handout:0>{\opensetc_1}
            \onslide*<0|handout:1>{Ob(\mathcal{\dbasec}^{\textcolor{base}{op}}) \ni \opensetc_1} 
            \onslide*<5-|handout:0>{\arrow[uu, "\sheafc_{\dbasec, \dtotalc}", maps to, color=sheaf]}
            \onslide*<0|handout:1>{\arrow[uu, "\sheafc_{\dbasec, \dtotalc}", maps to, color=sheaf, shift right = 10]}
            \onslide*<7-|handout:1>{\arrow[rr, "\iota"', hook, color=base]} \&   
            \onslide*<8-|handout:1>{\arrow[uu, "\sheafc_{\dbasec, \dtotalc}" description, maps to, color=sheaf]} \& 
            \onslide*<6-|handout:1>{\opensetc_2} 
            \onslide*<6-|handout:1>{\arrow[uu, "\sheafc_{\dbasec, \dtotalc}"', maps to, color=sheaf]}                   
            \end{tikzcd}
    \end{columns}
    \begin{center}
        \begin{alertblock}<8-|handout:1>{stalk}
            \begin{aligned*}
                \sheafc_{\dbasec, \dtotalc}\restriction_{\dbasepointc}\coloneqq \lim\limits_{\opensetc\ni \dbasepointc} \Gamma(\opensetc, \dtotalc\restriction_{\opensetc}) \approx \dfiberc_{\dbasepointc}
            \end{aligned*}
        \end{alertblock}

        \begin{alertblock}<9-|handout:1>{germ}
            \begin{aligned*}
                \dsectionc(\dbasepointc) \in \sheafc_{\dbasec, \dtotalc}\restriction_{\dbasepointc}
            \end{aligned*}
        \end{alertblock}
    \end{center}
\end{frame}

\begin{frame}{Sheaves}
    A sheaf is a presheaf that satisfies the following two axioms\cite{bakerMathsSheaf}\\
    \begin{block}<2-|handout:1>{locality}
        if $\mathcal{\opensetc} = \{\opensetc_i\}_{i\in I}$ is an open covering of \opensetc
        \onslide<3-|handout:1>{
        and if $\dsectionc^{a}, \dsectionc^{b} \in \sheafc(\opensetc_i)$ have the property $\dsectionc^{a}\restriction_{\opensetc_i} = \dsectionc^{b}\restriction_{\opensetc_i}$ for each $\opensetc_i \in \mathcal{\opensetc}$,}
        \onslide<4|handout:1>{ then $\dsectionc^{a} = \dsectionc^{b}$}
    \end{block} 
    \begin{block}<5-|handout:1>{gluing}
        if $\mathcal{\opensetc} = \{\opensetc_i\}_{i\in I}$ is an open covering of \opensetc\ and if $\dsectionc^{i} \in \sheafc(\opensetc_i)$ is given for each $i \in I$
        \onslide<6-|handout:1>{such that ${\dsectionc^{i}}\restriction_{\opensetc_i\cap \opensetc_j} = {\dsectionc^{j}}\restriction_{\opensetc_i \cap \opensetc_j}$ for each pair $\opensetc_i, \opensetc_j \in \mathcal{\opensetc}$,}
        \onslide<7-|handout:1>{ then there exists $\dsectionc \in \sheafc(\opensetc)$ such that $\dsectionc\restriction_{\opensetc_i} = {\dsectionc^{i}}$ for each $i \in I$} 
    \end{block}      
\end{frame}

\begin{frame}
    \frametitle<0|handout:1>{Functor: \vindexc: \mathcal{\gbasec} \rightarrow \mathcal{\dbasec}}
    \frametitle<0|handout:2>{Data}
    \frametitle<0|handout:3>{Pullback: data to region of the visualization} 
    \frametitle<0|handout:4>{Graphic}
    \frametitle<0|handout:5>{Pushforward: visualization to index of data}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
            \onslide*<7-8|handout:4>{\sheafc_{\gbasec, \gtotalc}} 
            \onslide*<7-8,10-|handout:5>{\arrow[rr, "\textcolor{functor}{\vindexpush}", color=functor]} \& \& 
            \onslide*<7-8|handout:5>{\textcolor{functor}{\vindexpush}\sheafc_{\gbasec, \gtotalc}}  
            \\
            \onslide*<2-|handout:1->{\gbasec}
            \onslide*<3-|handout:1->{\arrow[rr, "\vindex", color=functor]}
            \onslide*<7-8,10-|handout:4>{\arrow[u, "\sheaf_{\gbasec, \gtotalc}", maps to, color=sheaf]}
            \onslide*<6,8-9,11-|handout:3>{\arrow[d, dashed, maps to, color=sheaf]} \&  \& 
            \onslide*<1-|handout:1->{\dbasec}
            \onslide*<4-6,8-9,11-|handout:2-3>{\arrow[d, "\sheaf_{\dbasec, \dtotalc}", maps to, color=sheaf]}
            \onslide*<7-8,10-|handout:5>{\arrow[u, dashed, maps to, color=sheaf]} \\
            \onslide*<5-6,8|handout:3>{\textcolor{functor}{\vindexpull}\sheafc_{\dbasec, \dtotalc}} 
            \onslide*<5-6,8-9,11-|handout:3>{\arrow[rr, "\textcolor{functor}{\vindexpull}", color=functor]}  \& \& 
            \onslide*<4-6,8|handout:2-3>{\sheafc_{\dbasec, \dtotalc}}
        \end{tikzcd}
    \end{equation*}
    \only<4|handout:2>{
        \begin{itemize}
            \item $\dfiberc \hookrightarrow \dtotalc \xrightarrow{\pi} \dbasec$
            \item $\sheafc_{\dbasec, \dtotalc}:\opensetc \mapsto \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}}, \opensetc \subset \dbasec$
            \item $\cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} \ni \dsectionc: \opensetc \rightarrow \dfiberc\restriction_{\opensetc}$
            \item $\dsectionc(\dbasepointc) = \{f_0:v_0, \cdots,\}, \dbasepointc \in \opensetc$
        \end{itemize}
    }
    \only<6|handout:3>{
        \begin{itemize}
            \item $\vindexpullc\dfiberc \hookrightarrow \vindexpullc\dtotalc \xrightarrow{\pi} \gbasec$
            \item $\vindexpullc\sheafc_{\dbasec,\dtotalc}:\opensetgc \mapsto \cgamma{\opensetgc}{\vindexpullc\dtotalc\restriction_{\opensetgc}}, \opensetgc \subset \gbasec$
            \item $\cgamma{\opensetgc}{\vindexpullc\dtotalc\restriction_{\opensetgc}} \ni \vindexpullc\dsectionc: \opensetgc \rightarrow \vindexpullc\dfiberc\restriction_{\opensetgc}$
            \item $\vindexpullc\dsectionc(\gbasepointc) = \dsectionc(\vindexc(\gbasepointc)) = \dsectionc(\dbasepointc)$
        \end{itemize}
    }
    \only<7|handout:4>{
        \begin{itemize}
            \item $\gfiberc \hookrightarrow \gtotalc \xrightarrow{\pi} \gbasec$
            \item $\sheafc_{\gbasec, \gtotalc}:\opensetgc \mapsto \cgamma{\opensetgc}{\dtotalc\restriction_{\opensetgc}}, \opensetgc \subset \gbasec$
            \item $\cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}} \ni \gsectionc: \opensetgc \rightarrow \gfiberc\restriction_{\opensetgc}$
            \item $\gsectionc(\gbasepointc) = \{d_0, \cdots,\}, \dbasepointc \in \opensetfc$
        \end{itemize}
    }
